Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2016-11-07 Paper.tex
dinner

\section{Different architectures/Results}
\label{sec:results}
We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
archicture has the advantage of re-using a classical deep learning 
architecture with added on upsampling layer and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture, for a more detailed explaination please refer to \cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layer as one intends to learn 
the proper upsampling threw repeated deconvolution and convolution 
layers. This model can also be fine tuned, for more information please 
refer to the original paper \cite{noh2015learning}. We did not
ensemble classifier as suggested in 
\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores on the test sets.
% The final architecture that we tried is the UNet. This network combines 
%both contribution of the above networks, the UNet has a similar 
%architecture to the DeconvNet with skip layers.
\section{Result and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics other all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As we can not notice by the "holes" in 
the probability map when the interior of the cell is very bright. On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. Our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation or by simple 
visualation of the results.
\begin{table}
\begin{tabular}{|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN \\
 \hline
Accuracy  &       0.936 & 0.968 &0.958  \\
IU   &    0.759 &     0.856 & 0.857 \\
Recall     &       0.744  &     0.856 & 0.855 \\
Precision   &       0.741 &     0.858 & 0.878\\
F1    &       0.742 &     0.856 & 0.866 \\
TP       &       0.744 &     0.856 & 0.855  \\
TN      &       0.963 &     0.981 &  0.977\\
Performance    &       0.853 &     0.918 & 0.916\\
Pixel error  &  0.063 &     0.032 & 0.042\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}

>>>>

\section{Different architectures/Results}
\label{sec:results}
We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
archicture has the advantage of re-using a classical deep learning 
architecture with added on upsampling layer and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture, for a more detailed explaination please refer to \cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layer as one intends to learn 
the proper upsampling threw repeated deconvolution and convolution 
layers. This model can also be fine tuned, for more information please 
refer to the original paper \cite{noh2015learning}. We also did an
ensemble classifier of these two previous nets as suggested in 
\cite{noh2015learning}.
% The final architecture that we tried is the UNet. This network combines 
%both contribution of the above networks, the UNet has a similar 
%architecture to the DeconvNet with skip layers.
\section{Result and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics other all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As we can not notice by the "holes" in 
the probability map when the interior of the cell is very bright. On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. Our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation or by simple 
visualation of the results.
\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN & Ensemble\\
 \hline
Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
F1    &       0.742 &     0.856 & 0.866  & 0.863\\
TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
TN      &       0.963 &     0.981 &  0.977 & 0.979\\
Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}
